\documentclass[11pt]{article}
\usepackage{listings}
\usepackage{fullpage}
\usepackage{pdfsync}
\usepackage{subfigure}
\usepackage{boxedminipage}

%% \firstpageheader{\bf\Large CS 151}{\bf\Large Lab-2}{\bf\Large
%%   March 2, 2004}
%% \runningheader{CS 151}{}{Homework-TheLast}
%% \addpoints
\title{The Kevin Bacon Game}
\date{April 28, 2012}

\begin{document}

\maketitle 
%% \begin{center} %% \fbox{\fbox{\parbox{5.5in}{\centering This Exam is being given under %% the guidelines of the \textbf{Honor Code}. You are expected to 
%% respect those guidelines and to report those who do not. 
%% Answer the questions in the spaces provided. If you run out of 
%% room for an answer, continue on the back of the page. There are 
%% \numquestions\ questions for a total of \numpoints\ points.}}} 
%% \end{center}
\lstset{language=Python,numbers=left}

\section{Introduction}
You have may seen the commercial (http://www.youtube.com/watch?v=afJRKbBEr2Q) in which Kevin Bacon attempts to cash a check without ID.  In this commercial Bacon collects an unlikely combination of people with increasingly tenuous relationships that somehow wind up connecting him with the owner of the store.  So you see, he says, ``we are practically related!''  This idea caught on in Hollywood and if you've acted in a movie, your Kevin Bacon number is a reflection of how many links away from Kevin Bacon you are.  One actor is linked to another if they have acted in the same movie.  For example, Warwick Davis, who plays Marvin the Robot in the Hitchhikers guide to the Galaxy has a Kevin Bacon Number of 3.  Because Davis acted in Willow with Val Kilmer who acted with Bill Paxton in Tombstone, who acted with Kevin Bacon in Apollo 13.  

Your job is to write a program that allows the user to enter the name of an actor and then determines the Kevin Bacon number for that actor.  The program should print out the Kevin Bacon number for the actor and both the list of actors that form the chain and the movies they acted in together.

There are three data files for this assignment:  actors.dat, movies.dat, and movie\_actors.dat.  The first file contains a number for each actor along with their name. Notice that the number and name are separated by a $|$ to allow us to keep the spaces in the names.  You can still use the split method to break each line into a list of two elements. The second file contains a number that identifies each movie along with the title of the movie.  Again the numbers and titles are separated by a $|$.  
\vspace{.1in}


    \begin{minipage}[b]{0.33\textwidth}    
    \begin{verbatim}
2|Tim Allen
3|Tom Hanks
4|Don Rickles
5|Jim Varney
7|Jonathan Hyde
8|Bradley Pierce
9|Robin Williams
10|Kirsten Dunst
12|Jack Lemmon
13|Walter Matthau

   actors.dat
     \end{verbatim}
     \end{minipage}%%
    \begin{minipage}[b]{0.33\textwidth}
    \begin{verbatim}
1|Toy Story (1995)
2|Jumanji (1995)
3|Grumpier Old Men (1995)
4|Waiting to Exhale (1995)
5|Father of the Bride Part II (1995)
6|Heat (1995)
7|Sabrina (1995)
8|Tom and Huck (1995)
9|Sudden Death (1995)
10|GoldenEye (1995)
    
    movies.dat
     \end{verbatim}
     \end{minipage}%%
     \begin{minipage}[b]{0.33\textwidth}
        \begin{verbatim}
            1|2
            1|3
            1|5
            1|4
            2|10
            2|7
            2|8
            2|9
            3|12
            3|13
        
        movie_actors.dat
         \end{verbatim}
    \end{minipage}

The final file contains a movie number before the $|$ and an actor number after the $|$ This is the important file that you use to link one actor to another.  From the example in the movie\_actors.dat file you can see that there are four actors in movie 1 (Toy Story), therefore actor 2 (Tim Allen), 3 (Tom Hanks), 5 (Jim Varney), and 4 (Don Rickles) are all connected.  Looking at the file further you would see that (3) Tom Hanks and (63) Kevin Bacon are directly connected through Apollo 13.


There are three main problems to solve for this assignment:
\begin{enumerate}
    \item  Build a graph that represents the links between all the actors.  To build the graph you should use the Graph and Vertex classes found on the pythonworks.org website.  These classes are implemented just like the code in the textbook.  This is the most challenging part of the assignment.  You should start with a small part of the movies\_actors file and create a small graph.  Then use the Python environment to poke around at the graph and make sure that the links are correct.
    
    You will also want to build a Python dictionary that maps actor/movie numbers to their name/title.

    \item  Use the Breadth First Search algorithm to create the links from all actors back to Kevin Bacon.

    \item  Write a loop that allows the user to enter a name and see the Kevin Bacon number plus links.  You will need to implement the traverse function as described in the book to work backward from the actor entered to Kevin Bacon.
    
\end{enumerate}
Here is an example of the Kevin Bacon program in action.  Your program should produce output that is similar.
\begin{verbatim}
    host-17-15-55:python> python kevinbacon.py 
    What Actor would you like to trace? (exit to quit) Sidney Poitier
    The Kevin Bacon Number for  Sidney Poitier  is  3
    Sidney Poitier
       Shoot to Kill (1988)
    Tom Berenger
       Shattered (1991)
    Bob Hoskins
       Balto (1995)
    Kevin Bacon
    What Actor would you like to trace? (exit to quit)                              
\end{verbatim}

\section{Grading}
This program is due Friday May 11 at 5:00pm.

There are 30 points to this assignment:
\begin{itemize}
\item 15 points for correctly building and searching the graph
\item 10 points for traversing the searched graph
\item 5 points for good programming practice and style
\end{itemize}
\end{document}


% Local Variables:
% mode: LaTeX
% mode: Auto-Fill
% mode: RefTeX
% mode: Flyspell
% End:
